Sketch Recognition and Understanding

### 2009-04-28 draft/chapterSurvey.tex
before grammer before i pary

 A hybrid of PSO and other algorithms was investigated in various systems. \cite{} used a hybird of GA and PSO to breed solutions using GA then feed them to PSO. They domenstrated that using PSO-GA and PSO outperform using GA as an optimization algorithm.

 \subsection*{PSO neighbourhood topology}  
In general the PSO algorithm have fully connected particle which means that every particle know the global best and local best of each other particle. Other forms of cooperation and organizatoin were suggested in various systems.  \cite{} suggested to use a grid like topology where particle are connected to four other particles sround it. A ring  and star topology were widley used in \cite{}. In \cite{hiericalPSO}, Janson and Middendorf proposed to use a dynamic and hierrchinal neighbourhood structure. They showed that using such structure helps in mentainaing diversity over the solution space in a dynamic problem. % a PSO using a dynamic and hierarchical neighbourhood structure to handle dynamic optimization problems. They demonstrated that such a structure is useful for maintaining some particle diversity in a dynamic environment.

@@

change so that the optima can still be tracked.
One of the early works on using PSO for dynamic optimization
was by Eberhart and Shi in [13], where they used
an inertia weight version of PSO to track the optimum of
a 3-dimensional unimodal parabolic function which changes
its maxima every 100 iterations. It was found under certain
circumstances that the PSO’s performance was comparable
or better than that of previously published evolutionary algorithms
[1, 2].
For detection, Carlisle and Dozier used a sentry particle
which is randomly chosen at each iteration [10]. The sentry
particle gets evaluated before each iteration and compares
its fitness with its previous fitness value. If the two values
are different, indicating the environment has changed, ie.,
the optimum has moved, then the whole population gets
alerted and several possible responses can then be triggered.
Hu and Eberhart proposed to re-evaluate  pg and a second
best particle to detect if a change has occurred.
Various response strategies have also been proposed. Carlisle
and Dozier proposed to re-evaluate all pi of all particles when
a change has been detected [11]. If the re-evaluated pi is less
fit than its current position xi, then this pi is replaced by
its associated xi, because only these two evaluations can
be considered up-to-date. Hu and Eberhart studied the effects
of re-randomizing various proportions of the swarm to
maintain some degree of diversity in order to better track
the optima after a change [14]. However, this approach suffers
from possible information loss since the re-randomized
portion of the population does not retain any information
that might be useful from the past iterations.
In order to maintain better particle diversity throughout
a run, Blackwell and Bentley introduced charged swarms
where mutually repelling charged particles orbit a nucleus of
neutral particles (conventional PSO particles) [3]. Whereas
the charged particles allow the swarm to better adapt to
changes in the environment, the neutral particles play the
role of continuing to converge towards the optimum in finer
details.
Inspired by multi-population EA approaches such as the
multinational GA [22] and self-organizing scouts [7], Blackwell
and Branke proposed an interacting multi-swarm PSO
as a further improvement to the charged swarms [4]. The
multi-swarm PSO aims at maintaining multiple swarm populations
on different peaks. Multiple swarms are prevented
from converging to the same optimum by randomizing the
worse of two swarms that come too close. The multi-swarm
PSO also replaces the charged particles by quantum particles
whose position is solely based on a probability function
centered around the swarm attractor. The resulting multiquantum
swarms outperform charged and standard PSO on
the moving peaks function. This multi-swarm approach is
particularly attractive because of its improved adaptability
in a more complex multimodal dynamic environment where
multiple peaks exist and need to be tracked.
With a similar aim to locate and track multiple peaks
in a dynamic environment, Parrott and Li in [19, 20] proposed
a species-based PSO (SPSO) incorporating a speciation
algorithm first proposed by Petrowski [21]. The SPSO
uses a local “species seed” which provides the local  pg to
particles whose positions in the search space are within a
user-specified radius of the seed. This encourages swarms
to converge onto multiple local optima instead of a single
global optimum, hence developing multiple sub-populations
in parallel. In addition, the dynamic SPSO uses a parameter
pmax to limit the number of particles allowed in a species
(or swarm), with the excess particles reinitialized at random
positions in the total search space.

\subsection*{Particle Swarm Applications}
\label{sec:SwarmApp}
 Since 1995, when Kennedy and Eberhart \cite{PSOFirst,PSO2} introduced Particle Swarm Optimization Algorithm (PSO) the algorithm had been used in various systems. The algorithm was used to train Neural network in \cite{} and proved to perform better than GA algoirthm. In Image processing decipline PSO was used an optimization algorithm \cite{SwarmImageProcessing,Swarmimageprocessing2,Colorquantization,SwarmMedical}. PSO algorithm was used in \cite{PSOIMageClassification} to classify pixel to simplify the object segmentation process.

>>>>

 A hybrid of PSO and other algorithms was investigated in various systems. \cite{} used a hybird of GA and PSO to breed solutions using GA then feed them to PSO. They domenstrated that using PSO-GA and PSO outperform using GA as an optimization algorithm. 
  \subsection*{PSO neighbourhood topology}  
In general the PSO algorithm have fully connected particle which means that every particle know the global best and local best of each other particle. Other forms of cooperation and organizatoin were suggested in various systems.  \cite{} suggested to use a grid like topology where particle are connected to four other particles sround it. A ring  and star topology were widley used in \cite{}. In \cite{hiericalPSO}, Janson and Middendorf proposed to use a dynamic and hierrchinal neighbourhood structure. They showed that using such structure helps in mentainaing diversity over the solution space in a dynamic problem. % a PSO using a dynamic and hierarchical neighbourhood structure to handle dynamic optimization problems. They demonstrated that such a structure is useful for maintaining some particle diversity in a dynamic environment.

@@

There was various improvement used to improve the PSO algoirhtm. They moslty try to solve the problems premature coverge problem and increase the diversity of the particle population. Early work on dynamic optimization was introduced by Eberhard and shi \cite{paramterSelection}, where they added the inertia wegiht version of PSO to find the optimim of 3 dimentional function which change every 100 iteration.

\subsection*{Particle Swarm Applications}
\label{sec:SwarmApp}
 Since 1995, when Kennedy and Eberhart \cite{PSOFirst,PSO2} introduced Particle Swarm Optimization Algorithm (PSO) the algorithm had been used in various systems. The algorithm was used to train Neural network in \cite{PSOandNeuarl} and proved to perform better than GA algoirthm. In Image processing decipline PSO was used an optimization algorithm \cite{SwarmImageProcessing,Swarmimageprocessing2,Colorquantization,SwarmMedical}. PSO algorithm was used in \cite{PSOIMageClassification} to classify pixel to simplify the object segmentation process.
